### 2014-07-29 paper/paper.tex
Wrote a whole bunch for implementation

@@

The maximum entropy approach is well described in \cite{Pang2002} and
\cite{Nigam1999} and is summarized below.

@@

Where $Z(d)$ is a normalization function. $F_{i,c}$ is a feature function for
feature $f_{i}$ and class $c$.

>>>>

\subsection{Summary of Maximum Entropy}

@@

The maximum entropy approach is well described in \cite{Nigam1999} and is
summarized below. The training data is used to establish constraints in the
following fashion.

@@

Where $Z(d)$ is a normalization function, $F_{i,c}$ is a feature function for
feature $f_{i}$ and class $c$, and $\lambda_{i}$ is a feature parameter.

In order to establish reasonable $\lambda_{i}$ for each feature the Improved
Iterative Scaling is employed.

%TODO outline the IIS algorithm

\subsection{Implementation}

The classifier produced for this project is implemented in \textit{python} and make
extensive use of the \textit{nltk} (Natural Language Toolkit) library.

\begin{enumerate}

    \item \textbf{Tokenization} - The text is read into memory and separated into
        tokens. Each token represents an atom of text. Token types include
        word, number, user, hashtag, url, emoticon and punctuation.

    \item \textbf{Normalizing} - Each token is simplified to assist in
        classification by reducing the number of tokens.

        \begin{itemize}

            \item \textbf{Words} are coerced into lowercase

            \item \textbf{Numbers} are replaced with "\#NUM"

            \item \textbf{User} are replaced with "@USER"

            \item \textbf{Hashtags} are replaced with "\#OCTOTHORPE"

            \item \textbf{URLs} are replaced with "@URL"

            \item \textbf{Emoticon} are grouped into four different groups
                based on their intended meaning. Each group is then replaced
                with a representation. (e.g. `:)' $\rightarrow$ `EM\_HAPPY' and
                `;-p' $\rightarrow$ `EM\_WINK')

            \item most \textbf{Punctuation} is replaced with "PUNCT" however
                question marks, punctuation marks, and ellipsis are each
                replaced with their own representation.

        \end{itemize}

    \item \textbf{Feature Selection} - The number of tokens retained as
        features is further reduced.
        \begin{itemize}

            \item By \textbf{Removing Stopwords}, words that do not
                discriminate between classes are eliminated. Because of the
                limited size of the dataset only 28 stopwords are used.

            \item Then \textbf{Uncommon words} are removed. Words that do not
                meet a certain document frequency threshold are eliminated.
                Many of these words are proper nouns that, if retained are
                likely to cause the classifier to overfit to the training set

        \end{itemize}

    \item \textbf{Training}
    \item \textbf{Testing}
\end{enumerate}
